Case Study: 16S microbiome data (Schubert et al., 2014)

### 2018-02-26 datasets/microbiome/microbiome-goodrich.Rmd
Claire's edits to Patrick's edits

Here we download and analyze the Goodrich obesity (OB) dataset
[(Goodrich et al., 2014)](http://dx.doi.org/10.1016/j.cell.2014.09.053).
The dataset includes fecal samples from 428 individuals with low-to-normal body mass index (BMI < 25),
and 185 obese individuals (BMI > 30). We'll download the processed OTU tables from
Zenodo and unzip them in the `benchmark-fdr/datasets/microbiome/data` folder.

>>>>

Here we download and analyze the Goodrich obesity (OB) dataset
[(Goodrich et al., 2014)](http://dx.doi.org/10.1016/j.cell.2014.09.053).
The dataset includes fecal samples from 428 individuals with lean body mass index (BMI < 25),
and 185 obese individuals (BMI > 30). We'll download the processed OTU tables from
Zenodo and unzip them in the `benchmark-fdr/datasets/microbiome/data` folder.

We expect few or no truly differentially abundant OTUs ([Finucane et al., 2014](http://dx.doi.org/10.1371/journal.pone.0084689) and [Walters et al., 2014](https://dx.doi.org/10.1016%2Fj.febslet.2014.09.039)), so this study provides a real-life "null" example.

### 2018-02-26 datasets/microbiome/microbiome-schubert.Rmd
Claire's edits to Patrick's edits

@@

```{r, schubert-cleandata, eval=TRUE}
min_otu <- 10
min_sample <- 100

## Remove OTUs w/ <= min reads, samples w/ <= min reads
otu <- otu[rowSums(otu) > min_otu, ]
otu <- otu[, colSums(otu) > min_sample]

>>>>

Diarrhea comes with a broad community re-structuring, so we expect there to be many truly differentially abundant OTUs in this dataset.

@@

```{r, schubert-cleandata, eval=TRUE}
min_otu <- 10
minp_otu <- 0.01
min_sample <- 100

## Remove OTUs w/ <= min reads, w/ <= min prop, samples w/ <= min reads
otu <- otu[rowSums(otu) > min_otu, ]
otu <- otu[rowSums(otu > 0) / ncol(otu) > minp_otu, ]
otu <- otu[, colSums(otu) > min_sample]
